Blueprint

### 2020-11-26 blueprint.tex
Updates blueprint

\title{Blueprint}	
%\title{What is a Scheme in Algebraic Geometry?}
\author{Anthony Bordg}
\date{\today}
\maketitle

\begin{abstract}
% To be completed	
\end{abstract}

@@

\begin{construction}
	Let $X$ be a topological space and $\mathscr{F}$ a sheaf of rings on $X$. The set $I$ will denote a subset of the set of all open subsets of $X$. \\
	Given $U, V \in I$, $s \in \mathscr{F}(U)$ and $t \in \mathscr{F}(V)$,  we says that 
	$s \sim t$ if and only if there exists $W \in I$ such that $W \subseteq U \cap V$ and $s \restriction W = t \restriction W$. One checks that $\sim$ is an equivalence relation. \\
	Now, we consider the quotient of the disjoint union of the $\mathscr{F}(U)$'s.
	\[
	\varinjlim \mathscr{F}(U) \coloneqq \coprod_{U \in I} \mathscr{F}(U) \bigg/ \sim 
	\]
	Note that for any two elements $U, V \in I$, one has $[0_U] = [0_V]$ and $[1_U] = [1_V]$, where $[0_U]$ (\textit{resp.} $[1_U]$) denotes the class of the zero element (\textit{resp.} the multiplicative unit) of the ring $\mathscr{F}(U)$. \\
	Last, on each component $\mathscr{F}(U)$ the ring operations of $\varinjlim \mathscr{F}(U)$ are those of $\mathscr{F}(U)$. 
\end{construction}

\begin{ex}
	Prove $(\varinjlim \mathscr{F}(U), 0, +, 1, \times)$ is a ring. 
\end{ex}

\begin{definition}[direct limit]
	Let $X$ be a topological space, $\mathscr{F}$ a sheaf of rings on $X$ and $I$ a set of open subsets of $X$. The direct limit over $I$ is the ring $\varinjlim \mathscr{F}(U)$.
\end{definition}

@@

\begin{cons}

\end{cons}

>>>>

\title{Blueprint}
\author{Anthony Bordg}
\date{\today}
\maketitle

@@

\begin{construction}
	Let $X$ be a topological space and $\mathscr{F}$ a sheaf of rings on $X$. The set $I$ will denote a subset of the set of all open subsets of $X$. \\
	Given $U, V \in I$, $s \in \mathscr{F}(U)$ and $t \in \mathscr{F}(V)$,  we says that 
	$s \sim t$ if and only if there exists $W \in I$ such that $W \subseteq U \cap V$ and $s \restriction W = t \restriction W$. One checks that $\sim$ is an equivalence relation. \\
	Now, we consider the quotient of the disjoint union of the $\mathscr{F}(U)$'s.
	\[
	\varinjlim_I \mathscr{F}(U) \coloneqq \coprod_{U \in I} \mathscr{F}(U) \bigg/ \sim 
	\]
	Note that for any two elements $U, V \in I$, one has $[0_U] = [0_V]$ and $[1_U] = [1_V]$, where $[0_U]$ (\textit{resp.} $[1_U]$) denotes the class of the zero element (\textit{resp.} the multiplicative unit) of the ring $\mathscr{F}(U)$. \\
	Last, on each component $\mathscr{F}(U)$ the ring operations of $\displaystyle \varinjlim_{I} \mathscr{F}(U)$ are those of $\mathscr{F}(U)$. 
\end{construction}

\begin{ex}
	Prove $(\displaystyle \varinjlim_I \mathscr{F}(U), 0, +, 1, \times)$ is a ring. 
\end{ex}

\begin{definition}[direct limit]
	Let $X$ be a topological space, $\mathscr{F}$ a sheaf of rings on $X$ and $I$ a set of open subsets of $X$. The direct limit over $I$ is the ring $\displaystyle \varinjlim_I \mathscr{F}(U)$ or simply $\varinjlim \mathscr{F}(U)$.
\end{definition}

@@

\begin{cons}
	Let $(X, \mathscr{O}_X)$, $(Y, \mathscr{O}_Y)$ be two ringed spaces and $(f, \phi_f)$ a morphism between them. Given $x \in X$, consider 
	\[
	I \coloneqq \lbrace V \mid V \, \text{is an open neighborhhood of}\, f(x) \rbrace .
	\]
	Since we have a morphism $\phi_f: \mathscr{O}_Y \rightarrow f_* \mathscr{O}_X $ of sheaves on $Y$, we get a map between the direct limits over $I$. 
	\[
	(\mathscr{O}_Y)_{f(x)} \rightarrow \displaystyle \varinjlim_I \mathscr{O}_X (f^{-1} V)
	\]
	Last, there is a natural inclusion from $\displaystyle \varinjlim_I \mathscr{O}_X (f^{-1} V)$ to $(\mathscr{O}_X)_x$, so eventually we get an induced morphism of rings from $(\mathscr{O}_Y)_{f(x)}$ to $(\mathscr{O}_X)_x$ which we will denote $\phi_{f, x}$. 
\end{cons}
